MATH 3610 - Project \#1

### 2015-09-29 proj1.tex
added nontdimensionalizing

\begin{align*}
\frac{dI}{dt} & = - r S I \\
\frac{dS}{dt} & = r S I \\
\end{align*}

@@

\begin{align*}
\frac{dI}{dt} & = - r (K - I) I \\
\frac{dS}{dt} & = r S (K - S) \\
\end{align*}

@@

>>>>

\begin{align*}
\frac{dS}{dt} & = - r S I \\
\frac{dI}{dt} & = r S I \\
\end{align*}

@@

\begin{align*}
\frac{dS}{dt} & = - r S (K - S) \\
\frac{dI}{dt} & = r (K - I) I \\
\end{align*}

@@

\subsubsection{Nondimensionalizing the Model}

It would be helpful to make all of the constants dimensionless parameters.
This will give us insight into the different scales that the model works at.

To turn $I$ into a dimensionless parameter, we can divide by $K$.

\begin{align*}
\frac{d\left(\frac{I}{K}\right)}{dt} 
	& = \left( r K \right) \left( \frac{I}{K} \right) \left( 1 - \frac{I}{K} \right)\\
\frac{d\widetilde{I}}{dt} 
	& = \widetilde{r} \widetilde{I} \left( 1 - \widetilde{I} \right) 
\end{align*}

This shows that the dynamics of $I$ do not depend on its size.
For each value of the dimensionless constant $\widetilde{r}$,
	we determine the behavior from it.
